\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\usepackage{float}
\usepackage{hyperref}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\usepackage{listings}
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}
\lstset{style=mystyle}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}


\title{Problem Set 4}
\date{Due: December 4, 2022}
\author{Conor Twomey\\ Student No. 22996168\\
	Applied Stats/Quant Methods 1}


\begin{document}
	\maketitle
	\section*{Instructions}
	\begin{itemize}
		\item Please show your work! You may lose points by simply writing in the answer. If the problem requires you to execute commands in \texttt{R}, please include the code you used to get your answers. Please also include the \texttt{.R} file that contains your code. If you are not sure if work needs to be shown for a particular problem, please ask.
		\item Your homework should be submitted electronically on GitHub.
		\item This problem set is due before 23:59 on Sunday December 4, 2022. No late assignments will be accepted.
	\end{itemize}



	\vspace{.5cm}
\section*{Question 1: Economics}
\vspace{.25cm}
\noindent 	
In this question, use the \texttt{prestige} dataset in the \texttt{car} library. First, run the following commands:

\begin{verbatim}
install.packages(car)
library(car)
data(Prestige)
help(Prestige)
\end{verbatim} 


\noindent We would like to study whether individuals with higher levels of income have more prestigious jobs. Moreover, we would like to study whether professionals have more prestigious jobs than blue and white collar workers.

\newpage
\begin{enumerate}
	
	\item [(a)]
	Create a new variable \texttt{professional} by recoding the variable \texttt{type} so that professionals are coded as $1$, and blue and white collar workers are coded as $0$ (Hint: \texttt{ifelse}).
		\lstinputlisting[language=R, firstline=9, lastline=15]{ps04.R}
	\vspace{1cm}
	
	
	\item [(b)]
	Run a linear model with \texttt{prestige} as an outcome and \texttt{income}, \texttt{professional}, and the interaction of the two as predictors (Note: this is a continuous $\times$ dummy interaction.)
	
			\lstinputlisting[language=R, firstline=18, lastline=19]{ps04.R}
	
	\begin{table}[!htbp] \centering   \caption{}   \label{} \begin{tabular}{@{\extracolsep{5pt}}lc} \\[-1.8ex]\hline \hline \\[-1.8ex]  & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ \cline{2-2} \\[-1.8ex] & prestige \\ \hline \\[-1.8ex]  income & 0.003$^{***}$ \\   & (0.0005) \\   & \\  professional1 & 37.781$^{***}$ \\   & (4.248) \\   & \\  income:professional1 & $-$0.002$^{***}$ \\   & (0.001) \\   & \\  Constant & 21.142$^{***}$ \\   & (2.804) \\   & \\ \hline \\[-1.8ex] Observations & 98 \\ R$^{2}$ & 0.787 \\ Adjusted R$^{2}$ & 0.780 \\ Residual Std. Error & 8.012 (df = 94) \\ F Statistic & 115.878$^{***}$ (df = 3; 94) \\ \hline \hline \\[-1.8ex] \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ \end{tabular} \end{table} 
	
	\vspace{6cm}
	\item [(c)]
	Write the prediction equation based on the result.
	
		$$y = \beta_0 + \beta_1 x + \beta_2d + \beta_03xd$$
	$$y =21.142 + .003x + 37.781d + -.002xd$$
	\vspace{1cm}
	
	\item [(d)]
	Interpret the coefficient for \texttt{income}.
	\vspace{.5cm}
	
	For a one dollar increase, controlling for the type of work and the 
	interaction effect between income and type of work, there is a .003171
	increase in prestige.
	
	\vspace{1cm}	
	\item [(e)]
	Interpret the coefficient for \texttt{professional}.
	\vspace{.5cm}
	
	Being a white collar worker, controlling for the type of work and the 
	interaction effect between income and type of work, is associated with 
	a 37.781 increase in prestige.
	
\vspace{1cm}
	\item [(f)]
	What is the effect of a \$1,000 increase in income on prestige score for professional occupations? In other words, we are interested in the marginal effect of income when the variable \texttt{professional} takes the value of $1$. Calculate the change in $\hat{y}$ associated with a \$1,000 increase in income based on your answer for (c).
	\vspace{.5cm}
	
	d = 1 / yhat = (b0 + b2) + (b1 + b3)x
	
	 yhat = 21.142 + .003x + 37.781d + -.002xd
	 
	yhat = 21.142 + .003x + 37.781 (1) + -.002x(1)
	
	yhat = 21.142 + .003x + 37.781 - .002x 
	
	yhat = (21.142 + 37.781) + (.003x - .002x)
	
	yhat = 58.923 + .001x 
	
	yhat = 58.923 + .001(1000)
	
	yhat = 58.923 + 1
	
	yhat = 59.923
	
\newpage
	
	\item [(g)]
	What is the effect of changing one's occupations from non-professional to professional when her income is \$6,000? We are interested in the marginal effect of professional jobs when the variable \texttt{income} takes the value of $6,000$. Calculate the change in $\hat{y}$ based on your answer for (c).
	\vspace{.5cm}
	 when d = 0
	 
	 yhat = b0 + b1x + b2d + b3xd
	 
	yhat = 21.142 + .003x + 37.781d + -.002xd
	
	yhat = 21.142 + .003x + 37.781(0) +- .002x(0)
	
	yhat = 21.142 + .003x
	
	 yhat = 21.142 + .003(6000)
	 
	 yhat = 21.142 + 18
	 
	yhat = 39.142
	\vspace{1cm}
	
	
	 when d = 1
	 
	 yhat = 58.923 + .001(6000)
	 
	 yhat = 58.923 + 6
	 
	yhat = 64.923
		\vspace{1cm}
	
	 64.923 - 39.142
	 
	25.781
		\vspace{1cm}
		
	The marginal effect of changing from non-professional to professional when
	 income is $6,000$ is 25.781 increase in prestige. 
	
	
	
\end{enumerate}

\newpage

\section*{Question 2: Political Science}
\vspace{.25cm}
\noindent 	Researchers are interested in learning the effect of all of those yard signs on voting preferences.\footnote{Donald P. Green, Jonathan	S. Krasno, Alexander Coppock, Benjamin D. Farrer,	Brandon Lenoir, Joshua N. Zingher. 2016. ``The effects of lawn signs on vote outcomes: Results from four randomized field experiments.'' Electoral Studies 41: 143-150. } Working with a campaign in Fairfax County, Virginia, 131 precincts were randomly divided into a treatment and control group. In 30 precincts, signs were posted around the precinct that read, ``For Sale: Terry McAuliffe. Don't Sellout Virgina on November 5.'' \\

Below is the result of a regression with two variables and a constant.  The dependent variable is the proportion of the vote that went to McAuliff's opponent Ken Cuccinelli. The first variable indicates whether a precinct was randomly assigned to have the sign against McAuliffe posted. The second variable indicates
a precinct that was adjacent to a precinct in the treatment group (since people in those precincts might be exposed to the signs).  \\

\vspace{.5cm}
\begin{table}[!htbp]
	\centering 
	\textbf{Impact of lawn signs on vote share}\\
	\begin{tabular}{@{\extracolsep{5pt}}lccc} 
		\\[-1.8ex] 
		\hline \\[-1.8ex]
		Precinct assigned lawn signs  (n=30)  & 0.042\\
		& (0.016) \\
		Precinct adjacent to lawn signs (n=76) & 0.042 \\
		&  (0.013) \\
		Constant  & 0.302\\
		& (0.011)
		\\
		\hline \\
	\end{tabular}\\
	\footnotesize{\textit{Notes:} $R^2$=0.094, N=131}
\end{table}

\vspace{.5cm}
\begin{enumerate}
	\item [(a)] Use the results from a linear regression to determine whether having these yard signs in a precinct affects vote share (e.g., conduct a hypothesis test with $\alpha = .05$).
	\vspace{.5cm}
	
	Step 1 : 
	
   I am assuming the distribution is normal.
   
   \vspace{.5cm}
   Step 2 :
   
   The null hypothesis is vote share is not effected by lawn signs.
   
   The alternative hypothesis is that vote share is effected by lawn signs.
  
	\newpage		
	Step 3: 
	
	Calculate t-score 
	
		\lstinputlisting[language=R, firstline=83, lastline=86]{ps04.R}
		
		   \vspace{.5cm}
	Step 4:
	
	Calculate p-value for two-tailed test
	
	\lstinputlisting[language=R, firstline=90, lastline=93]{ps04.R}
	
	   \vspace{.5cm}
	Step 5: 
	
	Conclusion
	
	Because the p value is less than alpha (.05), we can reject
	 the null hypothesis.
	\vspace{1cm}
	\item [(b)]  Use the results to determine whether being
	next to precincts with these yard signs affects vote
	share (e.g., conduct a hypothesis test with $\alpha = .05$).
	
	\vspace{.5cm}
	
	Step 1 : 
	
	I am assuming the distribution is normal.
	
	\vspace{.5cm}
	Step 2 :
	
 The null hypothesis is vote share is not effected by lawn signs.
 
The alternative hypothesis is that vote share is effected by lawn signs.

		\vspace{.5cm}
	Step 3: 
	
	Calculate t-score 
	
	\lstinputlisting[language=R, firstline=112, lastline=115]{ps04.R}
		\newpage
	Step 4:
	
	Calculate p-value for two-tailed test
	
	\lstinputlisting[language=R, firstline=119, lastline=122]{ps04.R}
	\vspace{.5cm}
	Step 5: 
	
	Conclusion
	
	Because the p value is less than alpha (.05), we can reject
	the null hypothesis.
	\vspace{1cm}
	
	\item [(c)] Interpret the coefficient for the constant term substantively.
	\vspace{.5cm}
	
	When the all other covariates are zero, the constant 
	represents the predicted value for the outcome 
	 variable. So in this case, this is the predicted proportion
	of the vote share that went to McAuliff's opponent
	Ken Cuccinelli if there were no lawn signs at all.
	\vspace{1cm}
	
	\item [(d)] Evaluate the model fit for this regression.  What does this	tell us about the importance of yard signs versus other factors that are not modeled?
	\vspace{.5cm}
	
	The model has an Rsquared value of .092 which is very low.
	This means that the model does not account for much 
	of the variance which, unsurprisingly, indicates that other factors may be
	 at play for the swing to Cuccinelli other than one's proximity
	to a lawn sign.
	
	
\end{enumerate}  


\end{document}
